Price of Anarchy for Mean Field Games

### 2018-07-17 PoA.tex
problem with proposition 5!

\begin{proposition}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1> 0$, $b_2> 0$, $q_T+\bar{q}_T(1-s_T)>0$, and $q_T+\bar{q}_T(1-s_T)^2>0$ then 
	\begin{equation*}
	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{\bar{b}_2\to 0} > 1\qquad \text{and} \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:b2bar}
\end{proposition}
\begin{proof}
	First, we consider $\bar{b}_2 \to 0$. For every given $\bar{b}_2 >0$, we have existence and uniqueness of the solutions $u^{\bar{b}_2}_t$, $w^{\bar{b}_2}_t$ and $\eta^{\bar{b}_2}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}). Note that, as before, we have added the superscript $\bar{b}_2$ to emphasize the dependence on this parameter.

@@

	Let $u^{\bar{b}_2 \to 0}:[0,T]\to \mathbb{R}$ be the solution to the limiting Riccati equation:
	\begin{equation}
	\left({u}^{{\bar{b}_2 \to 0}}_t\right)' - 2A^u u_t^{\bar{b}_2 \to 0} +B^{\bar{b}_2 \to 0} (u_t^{\bar{b}_2 \to 0})^2+ C^{\bar{b}_2 \to 0}_u = 0, \qquad u_T^{r \to \infty} = D^{\bar{b}_2 \to 0}_u,
	\end{equation}
	which we recall has an explicit solution. It is easy to show that for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}u^{\bar{b}_2}_t=u^{\bar{b}_2 \to 0}_t$. Next, our goal is to bound $u^{\bar{b}_2}_t$ uniformly over $t \in [0,T]$ for small enough $\bar{b}_2$.

	Following the methodology of the proof of Proposition \ref{prop:r_bar_r}, let $\epsilon>0$. Then there is a $\bar{b}^*_2$ such that $\max_{\bar{b}_2<\bar{b}^*_2} \{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:c_1$. We have the following two inequalities for $\bar{b}_2<\bar{b}^*_2$ and $\forall t \in [0,T]$:
		\begin{IEEEeqnarray*}{rl}
			&\left\vert (C^{u,\bar{b}_2} + D^{u,\bar{b}_2} \delta^{+,\bar{b}_2}_u) - (C^{u,\bar{b}_2} + D^{u,\bar{b}_2} \delta^{-,\bar{b}_2}_u) e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u) (T-t)} \right\vert\\
			&\leq  c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2} \\
			&< \infty,
		\end{IEEEeqnarray*}
		and 
		\begin{IEEEeqnarray*}{rl}
			& \left\vert ( -\delta^{-,\bar{b}_2}_u + D^{u,\bar{b}_2} B^{\bar{b}_2} ) + (\delta^{+,\bar{b}_2}_u - D^{u,\bar{b}_2} B^{\bar{b}_2} ) e^{-(\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right\vert \\
			&\geq -2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} }\\
			&>  0.
		\end{IEEEeqnarray*}
		Thus, we can deduce that:
		\begin{IEEEeqnarray}{rCl}
			\vert u_t^{\bar{b}_2} \vert  &\leq& c_2,\ \forall t \in [0,T],\ \bar{b}_2<\bar{b}^*_2.  \nonumber
		\end{IEEEeqnarray}
	Similarly, for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}w^{\bar{b}_2}_t=w^{\bar{b}_2 \to 0}_t$, and  $w^{\bar{b}_2 \to 0}_t$ is uniformly bounded over $t \in [0,T]$ for small enough $\bar{b}_2$.

@@

	Now, for the case when $\bar{b}_2 \to \infty$,  we have $\lambda^{\bar{b}_2} \to 0$
	and $B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0$. It can be shown that:
	$$\lim_{\bar{b}_2 \to \infty}C^{u,\bar{b}_2}\sqrt{b_2+\bar{b}_2}=0,$$
	and
	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm \delta^{\bar{b}_2 \to \infty},$$
	and therefore,
	$$\lim_{\bar{b}_2 \to \infty} \delta^{\pm,\bar{b}_2}_u=\pm \infty,$$
	$$\lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{b_2 + \bar{b}_2}=0.$$
	Also, note from the assumptions $q_T+\bar{q}_T(1-s_T)>0$ and $q_T+\bar{q}_T(1-s_T)^2>0$, we have $D^u>0$ and $D^w>0$. From equation (\ref{eq:riccati_ut_sol}), for $t \in [0,T)$ we can deduce:
	\begin{equation*}
	\begin{split}
	 	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t =& \frac{ \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{+,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) - \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_u}{b_2 + \bar{b}_2} + \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right) + \left( \frac{\delta^{+,\bar{b}_2}_u}{b_2 + \bar{b}_2} - \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right)e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} }\\
	 	& \xrightarrow[\bar{b}_2 \to \infty]{} \delta^{\infty, \bar{b}_2} (r + \bar{r}(1-\bar{s})^2) ,
	 \end{split} 
	\end{equation*}
	where $\zeta = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) }{r+ \bar{r}(1-\bar{s})} (q_T + \bar{q}_T(1-s_T))$. 
	Thus, for $t \in [0,T)$, we have:
	\begin{equation*}
	B^{\bar{b}_2} u^{\bar{b}_2}_t=\frac{\sqrt{b_2+\bar{b}_2}}{r+\bar{r}(1-\bar{s})^2} \cdot (b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t \xrightarrow[\bar{b}_2 \to \infty]{}\infty.
	\end{equation*}
	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), we deduce: (ToDo: Nicolas, do you think this needs to be justified further? It seems obvious to me, but I'm not sure.)
	$$\lim_{\bar{b}_2 \to \infty} \bar{x}_t^{\bar{b}_2 \to \infty,MFG} = 0,\ \forall t \in (0,T]. $$	
	Similarly, we can show that for $t \in [0,T)$:
	\begin{equation*}
	\begin{split}
	(b_2 + \bar{b}_2) w^{\bar{b}_2}_t =&\frac{ \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{+,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) - \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{-,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T-t)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} + \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right) + \left( \frac{\delta^{+,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} - \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T-t)} }\\
	&\xrightarrow[\bar{b}_2 \to \infty]{} \sqrt{(r + \bar{r}(1-\bar{s})^2) C^w}.
	\end{split}
	\end{equation*}
	%Similar to the proof of Proposition \ref{prop:r_bar_r}, and using the assumptions $b_2>0$ and $q_T+\bar{q}_T(1-s_T)>0$, it can be shown that there exists a $c>0$ and $\bar{b}_2^*$ such that for $\bar{b}_2>\bar{b}^*_2$ and $\forall t \in [0,T]$:
	%\begin{equation*}
	%\begin{split}
	%|(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t| <& c, \\
	%|(b_2 + \bar{b}_2) w^{\bar{b}_2}_t| <& c, \\
	%|\bar{x}_t^{\bar{b}_2,MFG}|<&c.
	%\end{split}
	%\end{equation*}

	Next, our goal is to derive bounds for the functions $\frac{(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t}{\sqrt{b_2+\bar{b}_2}}$, $(b_2 + \bar{b}_2) w^{\bar{b}_2}_t$, and $\bar{x}_t^{\bar{b}_2,MFG}$. Let $0<\epsilon<\delta^{\bar{b}_2 \to \infty}$. We can check that there exists a $\bar{b}_2^*$ such that $ C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} <\epsilon$, and $\delta^{\bar{b}_2 \to \infty}-\epsilon<\left| \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}\right|< \delta^{\bar{b}_2 \to \infty} +\epsilon$ for $\bar{b}_2>\bar{b}_2^*$. Then we have for $t\in[0,T)$:
		\begin{equation*}
		\begin{split}
		\left| \frac{(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t}{\sqrt{b_2+\bar{b}_2}} \right| &\leq \frac{
			C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \left(\frac{\delta^{+,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} -\frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}\right)}{-\frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}}\\
		&\leq \frac{\epsilon + 2\epsilon\zeta}{\delta^{\bar{b}_2 \to \infty}-\epsilon} \\
		&=:c_1.
		\end{split} 
		\end{equation*}
	ToDo: other 2 function bounds

>>>>

\begin{proposition}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1> 0$, $q_T+\bar{q}_T(1-s_T)>0$, and $q_T+\bar{q}_T(1-s_T)^2>0$ then 
	\begin{equation*}
	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{\bar{b}_2\to 0} > 1\qquad \text{and} \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:b2bar}
\end{proposition}
\begin{proof}
	First, we consider $\bar{b}_2 \to 0$. For every given $\bar{b}_2 >0$, we have existence and uniqueness of the solutions $u^{\bar{b}_2}_t$, $w^{\bar{b}_2}_t$ and $\eta^{\bar{b}_2}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}). Note that, as before, we have added the superscript $\bar{b}_2$ to emphasize the dependence on this parameter.

@@

	Let $u^{\bar{b}_2 \to 0}:[0,T]\to \mathbb{R}$ be the solution to the limiting Riccati equation:
	\begin{equation}
	\left({u}^{{\bar{b}_2 \to 0}}_t\right)' - 2A^u u_t^{\bar{b}_2 \to 0} +B^{\bar{b}_2 \to 0} (u_t^{\bar{b}_2 \to 0})^2+ C^{\bar{b}_2 \to 0}_u = 0, \qquad u_T^{r \to \infty} = D^{\bar{b}_2 \to 0}_u,
	\end{equation}
	which we recall has an explicit solution. It is easy to show that for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}u^{\bar{b}_2}_t=u^{\bar{b}_2 \to 0}_t$. Next, our goal is to bound $u^{\bar{b}_2}_t$ uniformly over $t \in [0,T]$ for small enough $\bar{b}_2$, following the methodology of the proof of Proposition \ref{prop:r_bar_r}. Let $\epsilon>0$. Then there is a $\bar{b}^*_2$ such that $\max_{\bar{b}_2<\bar{b}^*_2} \{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:c_1$. We have the following two inequalities for $\bar{b}_2<\bar{b}^*_2$ and $\forall t \in [0,T]$:
		\begin{IEEEeqnarray*}{rl}
			&\left\vert (C^{u,\bar{b}_2} + D^{u,\bar{b}_2} \delta^{+,\bar{b}_2}_u) - (C^{u,\bar{b}_2} + D^{u,\bar{b}_2} \delta^{-,\bar{b}_2}_u) e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u) (T-t)} \right\vert\\
			&\leq  c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2} \\
			&< \infty,
		\end{IEEEeqnarray*}
		and 
		\begin{IEEEeqnarray*}{rl}
			& \left\vert ( -\delta^{-,\bar{b}_2}_u + D^{u,\bar{b}_2} B^{\bar{b}_2} ) + (\delta^{+,\bar{b}_2}_u - D^{u,\bar{b}_2} B^{\bar{b}_2} ) e^{-(\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right\vert \\
			&\geq -2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} }\\
			&>  0.
		\end{IEEEeqnarray*}
		Thus, we can deduce that:
		\begin{IEEEeqnarray}{rCl}
			\vert u_t^{\bar{b}_2} \vert  &\leq& c_2,\ \forall t \in [0,T],\ \bar{b}_2<\bar{b}^*_2.  \nonumber
		\end{IEEEeqnarray}
	Similarly, for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}w^{\bar{b}_2}_t=w^{\bar{b}_2 \to 0}_t$, and  $w^{\bar{b}_2 \to 0}_t$ is uniformly bounded over $t \in [0,T]$ for small enough $\bar{b}_2$.

@@

	Now, for the case when $\bar{b}_2 \to \infty$,  we have $\lambda^{\bar{b}_2} \to 0$
	and $B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0$. It can be shown that:
	$$\lim_{\bar{b}_2 \to \infty}C^{u,\bar{b}_2}\sqrt{b_2+\bar{b}_2}=0,$$
	and
	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm \delta^{\bar{b}_2 \to \infty},$$
	and therefore,
	$$\lim_{\bar{b}_2 \to \infty} \delta^{\pm,\bar{b}_2}_u=\pm \infty,$$
	$$\lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{b_2 + \bar{b}_2}=0.$$
	Also, note from the assumptions $q_T+\bar{q}_T(1-s_T)>0$ and $q_T+\bar{q}_T(1-s_T)^2>0$, we have $D^u>0$ and $D^w>0$. From equation (\ref{eq:riccati_ut_sol}), for $t \in [0,T)$ we can deduce:
	\begin{equation*}
	\begin{split}
	 	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t =& \frac{ \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{+,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) - \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_u}{b_2 + \bar{b}_2} + \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right) + \left( \frac{\delta^{+,\bar{b}_2}_u}{b_2 + \bar{b}_2} - \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right)e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} }\\
	 	& \xrightarrow[\bar{b}_2 \to \infty]{} \delta^{\infty, \bar{b}_2} (r + \bar{r}(1-\bar{s})^2) ,
	 \end{split} 
	\end{equation*}
	where $\zeta = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) }{r+ \bar{r}(1-\bar{s})} (q_T + \bar{q}_T(1-s_T))$. 
	Thus, for $t \in [0,T)$, we have:
	\begin{equation*}
	B^{\bar{b}_2} u^{\bar{b}_2}_t=\frac{\sqrt{b_2+\bar{b}_2}}{r+\bar{r}(1-\bar{s})^2} \cdot (b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t \xrightarrow[\bar{b}_2 \to \infty]{}\infty.
	\end{equation*}
	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), we deduce: (ToDo: Nicolas, do you think this needs to be justified further? It seems obvious to me, but I'm not sure.)
	$$\lim_{\bar{b}_2 \to \infty} \bar{x}_t^{\bar{b}_2 \to \infty,MFG} = 0,\ \forall t \in (0,T]. $$	
	Similarly, we can show that for $t \in [0,T)$:
	\begin{equation*}
	\begin{split}
	(b_2 + \bar{b}_2) w^{\bar{b}_2}_t =&\frac{ \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{+,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) - \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{-,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T-t)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} + \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right) + \left( \frac{\delta^{+,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} - \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T-t)} }\\
	&\xrightarrow[\bar{b}_2 \to \infty]{} \sqrt{(r + \bar{r}(1-\bar{s})^2) C^w},
	\end{split}
	\end{equation*}
	where we have used the fact that $\lim_{\bar{b}_2 \to \infty}\frac{\delta^{\pm,\bar{b}_2}_w}{b_2 + \bar{b}_2}=\sqrt{\frac{C^w}{r+\bar{r}(1-\bar{s})^2}}$ and therefore $\lim_{\bar{b}_2 \to \infty}\frac{\delta^{\pm,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2}=0$.

	Next, our goal is to derive bounds for the functions $\frac{(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t}{\sqrt{b_2+\bar{b}_2}}$, $(b_2 + \bar{b}_2) w^{\bar{b}_2}_t$, and $\bar{x}_t^{\bar{b}_2,MFG}$. Let $0<\epsilon<\delta^{\bar{b}_2 \to \infty}$. It is easy to check that there exists a $\bar{b}_2^*$ such that $ C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} <\epsilon$, and $\delta^{\bar{b}_2 \to \infty}-\epsilon<\left| \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}\right|< \delta^{\bar{b}_2 \to \infty} +\epsilon$ for $\bar{b}_2>\bar{b}_2^*$. Then we have for $\bar{b}_2>\bar{b}^*_2$ and $\forall t\in[0,T]$:
		\begin{equation*}
		\begin{split}
		\left| \frac{(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t}{\sqrt{b_2+\bar{b}_2}} \right| &\leq \frac{
			C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \left(\frac{\delta^{+,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} -\frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}\right)}{-\frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}}\\
		&\leq \frac{\epsilon + 2\epsilon\zeta}{\delta^{\bar{b}_2 \to \infty}-\epsilon} \\
		&=:c_1.
		\end{split} 
		\end{equation*}
	ToDo setup
	\begin{equation*}
	\begin{split}
		\left| (b_2 + \bar{b}_2) w^{\bar{b}_2}_t \right| &\leq \frac{ \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot\left( \frac{\delta^{+,\bar{b}_2}_w}{b_2 + \bar{b}_2}-\frac{\delta^{-,\bar{b}_2}_w}{b_2 + \bar{b}_2} \right)}{ \left(- \frac{\delta^{-,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} + \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right) + \left( \frac{\delta^{+,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} - \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T-t)} } \\
		& \leq \frac{}{0!!!}
	\end{split}
	\end{equation*}

	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and the non-negativity of $u^{\bar{b}_2}_t$, we have:
	\begin{equation*}
		\left| \bar{x}^{\bar{b}_2,MFG,}_t \right| \leq \left|\mathbb{E}(\xi)\right|e^{(b_1+\bar{b}_1)T}.
	\end{equation*}
